\documentclass{article}

\usepackage[margin=1in]{geometry}

\begin{document}

\noindent
\textbf{Title:}  \textsc{Underwater Stereo Cameras for 3D Reconstruction}

\noindent
\textbf{Brief Description:}


Package two commercial stereo camera systems for underwater use;
adapt and extend existing 3D software to perform realtime reconstruction.

\noindent
\textbf{Sponsor:}  UW-APL Science and Engineering Group (SEG)

\noindent
\textbf{Project Owners:}  Aaron Marburg (UW-APL)

\noindent
\textbf{Project Manager:} Aaron Marburg

\noindent
\textbf{Project Mission (what is the goal and how will you measure it?):}

Create a basic capacity to capture stereo imagery underwater (in limited circumstances), and
to process that imagery into 3D reconstructions.

\vspace{12pt}
\noindent
\textbf{Project Description (what is being created or changed and why?):}

Procure two commercial stereo cameras: a Sterolab Zed and a two-camera Elphel
camera processor.   Package them for underwater use and capture test imagery.
Leverage and extend existing reconstruction software packages can use to produce
3D models from the test video.

Deliverables:

\begin{itemize}
  \item For each stereo camera, a complete design for a packaged underwater housing w/ one working instance.
  \item Sample imagery from both cameras for subsequent testing and advertising.
  \item Intrinsic camera calibrations for all cameras in the water.
  \item Demonstrated capacity to produce 3D reconstructions from the camera video under a limited
  set of circumstances.
  \item Clear demonstration of the potential and further research challenges for underwater visual reconstruction.
\end{itemize}

\vspace{12pt}
\noindent
\textbf{High-Level Project or Product Requirements:  (Do you need equipment, staff or consultants?)}

\begin{itemize}
\item Mechanical and electrical engineering support for design and construction of underwater camera housings.
\item Machine shop services for construction of camera housings.
\item Personnel support for testing.
\end{itemize}

\vspace{12pt}
\noindent
\textbf{Values (operating guidelines):}

Open source or publicly publish as much as feasible.   Maintain focus on developing
basic capacity --- show that it can be done, with goal of getting continued work to pay for
further iteration and refinement.

\vspace{12pt}
\noindent
\textbf{Boundaries (givens):}

Fixed budget.

\vspace{12pt}
\noindent
\textbf{Barriers (need to overcome):}

Limited time to work on project.  Limited support (e.g. no other programmers).

\vspace{12pt}
\noindent
\textbf{Influencers:}

\begin{itemize}
\item Andy, other APL PIs
\item SEG leadership
\item Potential sponsors (ONR?)
\end{itemize}

\vspace{12pt}
\noindent
\textbf{Summary Budget:}

\$18,813 total, as laid out in proposal.

\vspace{12pt}
\noindent
\textbf{Initial Risks  (from leadership perspectives, what high level “gotchas” that can trip up your project?):}

Adaptation of existing SLAM software will still be very time intensive, and may
not work well at first.   Starting again from first principles doesn't makes
sense, but by adopting existing work there is a large start-up transient and
still the need to make application-specific  modifications to the framework.

\vspace{12pt}
\noindent
\textbf{Summary milestones  (What are key dates?  Regulatory, political, seasonal, payment dates, major project work completion dates):}

\begin{tabular}{lp{0.75\textwidth}}
Febuary 2016 & Project kick-off \\
June 2016 & In-pool imaging of RSN equipment in the OSB test tank. \\
Sept 2016 & Completion of project report.
\end{tabular}

\vspace{12pt}
\noindent
\textbf{Success Indicators (what is the definition of success for the sponsor and owners?):}

Demonstrate and publicizing (academic or otherwise) a capacity for underwater
stereo imaging and 3D reconstruction.

\vspace{12pt}
\noindent
\textbf{Order of priorities in the iron triangle (scope,cost,schedule)?}

Cost $>$ schedule $>$ scope?


\end{document}
